Meritorcacy Scale: Preferences and Perceptions

### 2019-11-18 index.Rmd
update1119

---
title: "Pre-reg, scale perception meritocracy"
author:
- Luis Maldonado
- Juan Carlos Castillo
- Julio Iturra
- Jorge Atria
- Francisco Meneses
date: "13-11-2019"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: false
---

>>>>

---
title: "Meritorcacy Scale: Preferences and Perceptions"
csl: apa6.csl
bibliography: zlibrary.bib
css: style.css
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
    toc_depth: 2
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---

```{r eval=FALSE, echo=FALSE}
# Para obtener doble output (html/pdf) correr directamente en consola/terminal:
rmarkdown::render('pre-reg_merir-scale.rmd', output_format = 'all')
```
